PCA

### 2019-10-16 analysis/11_pcalda.Rmd
new pca plots

mypcadf <- data.frame(PC1 = mypca$x[, 1], PC2 = mypca$x[, 2], PC3 = mypca$x[, 3], 
                  PC4 = mypca$x[, 4],PC5 = mypca$x[, 5],PC6 = mypca$x[, 6],
                  ID = row.names(countData))
head(mypcadf)
mypcadf$V1 <- row.names(mypcadf)
mypcadf <- left_join(colData, mypcadf)
head(mypcadf)

a <- ggplot(mypcadf, aes(x = PC1, y = PC2, color = colData$treatment)) +
  geom_point() + labs(x = "PC1: 36%", y = "PC2: 32%")
b <- ggplot(mypcadf, aes(x = PC3, y = PC4, color = colData$treatment)) +
  geom_point() + theme(legend.position = "bottom", legend.title = element_blank()) + labs(x = "PC3: 25%", y = "PC4: 3%")

mylegend <- get_legend(b)

ab <- plot_grid(a + theme(legend.position = "none") ,
                b + theme(legend.position = "none"))

plot_grid(ab,mylegend, ncol = 1, rel_heights = c(0.9,0.1))

fviz_pca_var(res.pca, col.var="contrib") +
scale_color_gradient2(low="white", mid="blue", 
      high="red", midpoint=50) + theme_minimal()

>>>>

mypcadf <- data.frame(PC1 = mypca$x[, 1], PC2 = mypca$x[, 2], PC3 = mypca$x[, 3], 
                  PC4 = mypca$x[, 4],PC5 = mypca$x[, 5],PC6 = mypca$x[, 6],
                  ID = row.names(countData))

mypcadf$V1 <- row.names(mypcadf)
mypcadf <- left_join(colData, mypcadf)

a <- ggplot(mypcadf, aes(x = PC1, y = PC2, color = colData$treatment)) +
  geom_point() + labs(x = "PC1: 35.9%", y = "PC2: 32.5%") + theme_minimal(base_size = 8)  +
  theme(legend.title = element_blank(), legend.position = "left")

b <-  fviz_pca_var(mypca,  labelsize = 3 , axes.linetype = "blank")

ab <- plot_grid(a,b + theme(axis.text = element_blank()) + ggtitle(NULL), rel_widths = c(0.6,0.4))
ab
